%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Friggeri Cover Letter
% XeLaTeX Template
% Version 1.0 (1/11/15)
%
% This template has been downloaded from:
% https://github.com/mlda065/friggeri-letter
%
% Original author:
% Matthew Davis, based on code by
% Adrien Friggeri (adrien@friggeri.net)
% https://github.com/afriggeri/CV
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important notes:
% This template needs to be compiled with XeLaTeX
% You may need to compile twice for the header to appear.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[a4paper,english]{friggeri-letter}

\usepackage{babel}

\begin{document}

\header{ryan}{grose}{aspiring software engineer}

\address{
   6200 Norma Beach Rd. \\
   Edmonds, WA 98026
}


\letter{
   Disney Enterprise Technology Engineering \\
   925 4th Ave \#1600 \\
   Seattle, WA 98104
}





\opening{Dear Emerging Technology Team:}

My name's Ryan Grose and I'm really excited to be applying for the Enterprise Technology Engineering Internship. I love both Disney and innovative technology so when I saw your post on indeed my heart raced a bit. With this excitement and my experience in machine learning and software development, I can be both a contributing member and a pleasure to work with.

Most of my experience has been in collaborative coding and research projects, including a chess-playing ai in a cloud framework. For this we used Google's cloud compute engine to run and analyze the performance of parallelized chess ai algorithms using different search techniques, memory space, and number of cores. We then communicated these results in a paper and presentation.

This example demonstrates key advantages I can bring as an intern. First, I can work well with others whether that's communicating responsibilities or using proper version control. Second, I can communicate findings, ideas, and code to others. Finally, I can think on my feet. Since we were testing techniques and using technologies that were new (to us) we had to be able to digest new information quickly. As an intern I hope to encounter and learn new things often so this skill becomes all the more useful.

Currently I'm a computer science student at the University of Washington. This last year I took part in an exchange program with the Royal Institute of Technology (aka KTH) in Stockholm. As an ending to this I'm backpacking around Europe until I return at the end of September to work and finish my studies. This would therefore be the earliest time that I could meet in person, but I'm available via email at ryan@grose.in and can arrange a phone or skype interview nearly anytime. For work hours I'm similarly available anytime. If offered this position, I will be ready to hit the ground running and grow through the opportunity to work in Disney's team of talented engineers. I look forward to hearing back from you soon.


\closing{
   Yours Sincerely\\
   Ryan Grose}

\end{document}
