%!TEX TS-program = xelatex
\documentclass[]{friggeri-cv}
% \usepackage{fontawesome}
% \addbibresource{bibliography.bib}

\begin{document}
\header{devan}{grose}
       { software engineer | web developer }




% In the aside, each new line forces a line break
\begin{aside}
  \section{contact}
    6200 Norma Beach Rd
    98026 Edmonds
    Washington
    ~
    425.361.6022
    \href{mailto:devangrose@gmail.com}{devangrose@gmail.com}
    \href{http://devangrose.me}{devangrose.me}
    ~
    linkedin.com/in/devangrose
    github.com/devangrose
  \section{programming}
    react
    AWS (Cloudfront, Lambdas/SNS/SQS)
    C\#
    monadic/functional concepts
    git
    postgres
    jquery
    html/css
    nodejs

\end{aside}

\section{experience}

\begin{entrylist}
  \entry 
    {jan 2018 -}
    {Software Developer}
    {Navex Global}
    {Increased department-wide developer efficiency by establishing standards/patterns for ReactJS with Redux. Drove innovation by prototyping new UI concepts. Created component libraries and refactored to make future code more efficient, readable, and correct across the platform.\\
    Reduced errors and maintenance using a monadic API with behavior driven development standards.\\
    Owned agile epics; wrote stories, estimated time cost across multiple teams, and parallelized work to meet deadlines.
    }
  
  \entry 
    {2018 - }
    {Owner | Developer}
    {Code Solutions, LLC}
    {Drove web traffic and sales to small businesses by building simple, mobile-first, single page solutions using Material Design. \\
    Enabled online sales via low maintenance AWS serverless infrastructure with ReactJS and Python. \\
    Scaled out business capabilities by managing small Designer/Developer pairs. Aligned business values through clear communication with clients.}

 
  \entry
    {2012 -}
    {STEM Mentor Volunteer}
    {}
    {Hosted Q/A sessions at bootcamps, mentored recent graduates in establishing careers, and led youth day camps inspiring and educating for Computer Science.\\
    Taught computer science and math to students of all ages. Subjects ranged from algebra to business stastics and data structures.}

%  \entry
%    {2012 - 2019}
%    {Lifeguard and Swim Instructor}
%    {Washington Athletic Club}
%    {Taught swimming to people of all ages and disabilities.}
%
%  \entry
%    {2014}
%    {Coding Competition: 1st Place}
%    {TEALS at UW}
%    {Won 1st place in a team coding competition sponsored by Microsoft with over 50 teams.}
  

\end{entrylist}

\section{projects}

\begin{entrylist}

  \entry
    {aug 2018}
    {Internet Rover}
    {Bootcamp Project}
    {Built a rover using a Raspberry Pi and allowed piloting through my web site using an API written using NodeJS and Postgres.}

  \entry
    {july 2018}
    {Front End Game}
    {Personal Project}
    {Designed and implemented a reimagined, scalable version of the popular mobile game 2048. Used jQuery, javascript, html, and css.}

\end{entrylist}


\section{education}

\begin{entrylist}
  \entry
    {2014-2016}
    {Washington State University}
    {}
    {Studied data strutures, algorithms, and computer science fundamentals.}
  \entry
    {2018}
    {General Assembly}
    {Web Development Immersive}
    {Studied web development. Including NodeJS, Django, React, jQuery, Postgres.}

\end{entrylist}


\end{document}